---
title: "Lab 01 - Hello R"
author: "Thomas Huang"
date: "2026-01-16"
output: 
  html_document: 
    highlight: zenburn
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
data("datasaurus_dozen")
```

## Exercises

### Exercise 1

```{r}
glimpse(datasaurus_dozen)
```
There are 1,846 rows and 3 columns.

### Exercise 2

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
By looking at the plot, there is no visually observable linear patterns of $y$ and $x$. There is a weak correlation between $y$ and $x$, $r = -.064$.


### Exercise 3

Below codes visualize $y$ and $x$ in the star dataset.

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculate the correlation.

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```
Similar to the last question,  there is no visually observable linear patterns of $y$ and $x$. There is a weak correlation between $y$ and $x$, $r = -.063$.

### Exercise 4

```{r plot-circle}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-cirlce}
dino_data %>%
  summarize(r = cor(x, y))
```
Similar to the last question,  there is no visually observable linear patterns of $y$ and $x$. There is a weak correlation between $y$ and $x$, $r = -.068$.

### Exercise 5

```{r plot-all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
All 13 datasets show cool visual patterns of $y$ and $x$ but without clear linear patterns. All 13 datasets show weak correlations between $y$ and $x$, with $r$ ranging from $-.060$ to $-.069$.


