---
title: "Lab 01 - Hello R"
author: "Thomas Huang"
date: "2026-01-16"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
data("datasaurus_dozen")
```

## Exercises

### Exercise 1

```{r}
glimpse(datasaurus_dozen)
```
There are 1,846 rows and 3 columns.

### Exercise 2

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
By looking at the plot, there is no visually observable linear patterns of $y$ and $x$. There is a weak correlation between $y$ and $x$, $r = -.064$.


### Exercise 3

Below codes visualize $y$ and $x$ in the star dataset.

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculate the correlation.

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```
Similar to the last question,  there is no visually observable linear patterns of $y$ and $x$. There is a weak correlation between $y$ and $x$, $r = -.063$.

### Exercise 4

```{r plot-circle}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-cirlce}
dino_data %>%
  summarize(r = cor(x, y))
```
Similar to the last question,  there is no visually observable linear patterns of $y$ and $x$. There is a weak correlation between $y$ and $x$, $r = -.068$.

### Exercise 5

This is your final exercise! Add code and narrative as needed. Be creative and show off what you’ve learned so far.
Add code and narrative as needed.

To add additional R chunks, you can either type the backticks, curly braces, and the letter `r`, or use the "Insert Chunk" button above (the green C+ icon). Have fun!


